%Empieza configuracion
\setstretch{1.0}
\titleformat{\chapter}{\Huge\bfseries}{\thechapter}{0 pt}{\rule{340 pt}{3 pt}\\}
\titlespacing{\chapter}{100 pt}{-25 pt}{40 pt}[10 pt]	
\pagestyle{fancy}
\fancyhead[RO,RE]{\thepage}
\fancyfoot[CO,CE]{}
%Termina configuracion

\chapter*{Motivation}
\addcontentsline{toc}{chapter}{Motivation}
\setstretch{1.5} %Regresa el interlineado a 1.5

\normalsize
\noindent

We live in a world full of compute and sensing devices, not just the personal
computers used for work or school. Every day we are in contact with compute and
sensing devices everywhere. Just in the early morning jogging, our activity
could be tracked by multiple sensors that measure our distance, speed and
calories consumed during the exercise. All these devices provided with unique
identifiers and the ability to transfer data over a network are part of the
Internet of Things (IoT) technology. 

The IoT systems are much more than just the compute and sensing devices. There
must be a part that storage and process the information gathered from all the
sensors  in order to display the meaningful information on an easy to access
user interface. 

The use of IoT devices is rising quickly, as well as its problems. According to
\cite{Benkhelifa} by 2022 it is expected to have 14 billions of IoT devices. As
you can imagine, the rise of IoT will lead to an explosion in the volume of
data collected, transmitted and processed. Besides that, the power consumption
of the compute systems that store and process the data generated by the IoT
devices is a key part to considerate. If current trends continue, a system to
handle the IoT data will require 100 megawatts \cite{Xizhou}.

However the computational power that the IoT systems might be enough to
process all the data they generate. As  theoretical physicist Michio Kaku
mention in \cite{Michio}: \textit{"Today, your cell phone has more computer
power than all of NASA back in 1969, when it placed two astronauts on the
moon"}. This fact motivated us to wonder if it is possible that a network of IoT
systems could process the data they generate on their own at real time. In
order to answer that question it is necessary to make a technical comparison
between a network of IoT systems and a traditional computing system used for
storage and processing of data incoming from IoT devices. 

This encouraged us to work in the development of a
methodology that helps others in the IoT industry to determine if it is
necessary to send the sensors data to a centralized processing system or it can
be managed by a network of IoT computing systems. 

\clearpage
